The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-23 paper.tex
update

  We tabulate parameters in the first four\
  categories in \Cref{table-parameters},\
  except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
  can be derived from the known parameters and pressure equilibrium condition\
  on the interfaces $(z=\pm z_{0})$ between the disk and atmosphere.\

>>>>

  We tabulate parameters in the first four\
  categories of \Cref{table-parameters},\
  except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
  can be derived from the known parameters and pressure equilibrium condition\
  on the interfaces $(z=\pm z_{0})$ between the disk and atmosphere.\
